---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rseismTLS

<!-- badges: start -->
<!-- badges: end -->

The rise in the frequency of anthropogenic earthquakes due to deep fluid injections is posing serious economic, societal, and legal challenges to many geo-energy and waste-disposal projects. Existing Traffic Light Systems (TLSs) to assess such problems are still inherently heuristic and mostly based on expert elicitation (so-called clinical judgment). The \code{rseismTLS} package provides actuarial tools to analyse, forecast and mitigate induced seismicity during underground stimulation. It includes a risk module to define the TLS based on safety criteria. The proposed dynamic TLS framework is based on the work initiated by Mignan et al. (2015; 2017; 2019a; 2019b).

## Disclaimer

The rseismTLS package is provided "as is", without warranty of any kind. In no event shall the author or copyright holder be liable for any claim, damages or other liability (see MIT license LICENSE file).

## Installation

You can install rseismTLS from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("amignan/rseismTLS")
```

## In construction

Please come back later - this package is still under construction

